---
title: "Fav_NBA_Players_Demo_Analysis"
output: pdf_document
---
```{r, echo=FALSE}
setwd("~/Documents/MIDS/w251/basketball/hakeem")
data.yrly <- read.csv("olajuha01_seasonlogs.csv")
```

##Player 1: Hakeem Olajuwon

```{r, echo=FALSE}
par(mfrow=c(3,2))
barplot(data.yrly$pts_per_g, names.arg = data.yrly$season, main = "Points per Game, by Season", xlab = "Season", ylab = "Points", col="red")
barplot(data.yrly$trb_per_g, names.arg = data.yrly$season, main = "Total Rebounds per Game, by Season", xlab = "Season", ylab = "Rebounds", col="gray")
barplot(data.yrly$ast_per_g, names.arg = data.yrly$season, main = "Assists per Game, by Season", xlab = "Season", ylab = "Assists", col="blue")
barplot(data.yrly$stl_per_g, names.arg = data.yrly$season, main = "Steals per Game, by Season", xlab = "Season", ylab = "Steals", col="green")
barplot(data.yrly$blk_per_g, names.arg = data.yrly$season, main = "Blocks per Game, by Season", xlab = "Season", ylab = "Blocks", col="orange")
barplot(data.yrly$tov_per_g, names.arg = data.yrly$season, main = "Turnovers per Game, by Season", xlab = "Season", ylab = "Turnovers", col="purple")
```

How big of an offensive load did Olajuwon take over the years? And what kind of offensive load?

```{r, echo=FALSE}
par(mfrow=c(3,2))
plot(data.yrly$fg2_pct, main = "2 Pt Field Goal %, by Season (1984-2002)", ylab = "2 Pt FG %", cex=.6, col='blue', pch=19)
plot(data.yrly$fg2a_per_g, main = "2 Pt Field Goal Attempts, by Season (1984-2002)", ylab = "2 PtFGA", cex=.6, col='lightblue', pch=19)
plot(data.yrly$fg3_pct, main = "3 Pt Field Goal %, by Season (1984-2002)", ylab = "3 Pt FG %", cex=.6, col='red', pch=19)
plot(data.yrly$fg3a_per_g, main = "3 Pt Field Goal Attempts, by Season (1984-2002)", ylab = "3 Pt FGA", cex=.6, col='orange', pch=19)
plot(data.yrly$ft_pct, main = "Free Throw %, by Season (1984-2002)", ylab = "FG %", cex=.6, col='darkgreen', pch=19)
plot(data.yrly$fta_per_g, main = "Free Throw Attempts, by Season (1984-2002)", ylab = "FTA", cex=.6, col='lightgreen', pch=19)
```

How has Olajuwon improved over the years?

What was his peak year?



What kind of player did he turn into?
-looking at trends of his major stats, can we see whether or not he became more of a scorer as time went on, more aggressive to the rim (more fta) or more efficient w the ball, less fouls, more healthy, etc?

What about Olajuwon made him truly great? Can we tell from his stats?

What was his biggest night, statistically, in terms of:
-points
-rebounds
-assists
-blks
-stls

In 1993:

Trend of ppg of gamelogs w highest win share - 1993

What was his peak game?

How many double doubles did he have?

How many triple doubles?

How many quadruple doubles?
